---
output:
  html_document: default
  pdf_document: default
---
# User study Intelligent Task Management and Visualisation: Evaluation

## Visualisation

### Task 1.1 - Extended Nasa-TLX
```{r}
getwd()
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)

nasa_tlx <- read_excel("data/data_prepared.xlsx", sheet="task_1_ext_nasa_tlx")

data <- nasa_tlx %>%
  pivot_longer(cols = c(`Workload`, `Sense of control`, `Creativity Support Index`), names_to="variable", values_to="value") %>%
  group_by(variable) %>%
  summarize_at(vars(value), list(~mean(.), ~sd(.), ~n())) %>%
  arrange(factor(variable, levels = c("Workload", "Sense of control", "Creativity Support Index")))

data

plot <- data %>%
  ggplot( aes(x=factor(variable, level=variable), y=mean, fill=variable)) + 
  geom_bar(position="dodge", stat="identity", width = 0.6) + 
  geom_text(aes(label = round(mean, 2)), vjust=-0.5, hjust = -0.5) + 
  geom_errorbar(aes(x=variable, ymin=mean-sd, ymax=mean+sd), width=0.2) + 
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80, 100), limits=c(0,100)) +
  xlab(" ") + ylab("Mean") +
  guides(fill="none") +
  theme_minimal() +
  scale_fill_manual("legend", values = c("Workload" = "#c8d5b9", "Sense of control" = "#8fc0a9", "Creativity Support Index" = "#68b0ab"))

print(plot)

ggsave("plots/bar_nasa_tlx.eps",
       plot = plot,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       limitsize = TRUE)
```

### Task 1.1 - Number of events by prior experience 
```{r}
getwd()
library(readxl)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(stringr)

events <- read_excel("data/data_prepared.xlsx", sheet="task_1_events")

data_by_used <- events %>%
  pivot_longer(cols=c(4:11), names_to="variable", values_to="value") %>%
  group_by(`Used before`, variable) %>%
  summarise_at(vars(value), list(~mean(.), ~sd(.), ~n()))

data_all <- events %>%
  pivot_longer(cols=c(4:11), names_to="variable", values_to="value") %>%
  group_by(variable) %>%
  summarise_at(vars(value), list(~mean(.), ~sd(.), ~n())) %>%
  add_column(`Used before`=2, .before=1)

data <- rbind(data_by_used, data_all)

data

plot <- data %>%
  ggplot(aes(x=reorder(variable, -mean), y=mean, fill=factor(`Used before`))) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(.9)) + 
  xlab("Action type") + ylab("Actions") +
  theme_minimal() +
  theme(legend.position="top") + 
  scale_fill_manual(values=c("#d8b365", "#5ab4ac","#e5e5e5"), 
                    name="Have you used board based tools before?",
                    labels=c("no (n=3)", "yes (n=10)", "combined (n=13)")) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

print(plot)

ggsave("plots/bar_events_by_exp.eps",
       plot = plot,
       device = "eps",
       scale = 1, units = "cm",
       height = 12,
       dpi = 300,
       limitsize = TRUE)
```

### Task 1.2 - Nesting comparision
```{r}
getwd()
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)

level <- read_excel("data/data_prepared.xlsx", sheet="task_1_level")

data <- level %>% pivot_longer(cols=-c(`Participant ID`), names_to="variable", values_to="value") %>% 
  group_by(variable) %>% 
  summarize_at(vars(value), list(~mean(.), ~sd(.), ~n())) %>%
  arrange(factor(variable, levels = c("Standard", "Personal", "Favourite of proposed", "Favourite overall")))

data

#colors <- c("Standard" = "#D1D5DB", "Personal" = "#71c3d6", "Favourite of proposed" = "#407ebd", "Favourite overall" = "#273066")
# https://coolors.co/f7ecca-c8d5b9-8fc0a9-68b0ab-4a7c59
colors <- c("Standard" = "#F7ECCA", "Personal" = "#c8d5b9", "Favourite of proposed" = "#8fc0a9", "Favourite overall" = "#68b0ab")

plot <- data %>%
  ggplot(aes(x=factor(variable, level=variable), y=mean, fill=variable)) + 
  geom_text(aes(label = round(mean, 2)), vjust=-0.5, hjust = -0.5) + 
  geom_bar(stat="identity", position = "dodge", width = 0.7) + 
  geom_errorbar(aes(x=variable, ymin=mean-sd, ymax=mean+sd), width=0.2) + 
  xlab("Arrangement") + ylab("Nesting level") +
  guides(fill="none") +
  theme_minimal() +
  scale_fill_manual("legend", values = colors)

data2 <- level %>% pivot_longer(cols=-c(`Participant ID`), names_to="variable", values_to="value")

fun_mean <- function(x){
  return(data.frame(y=mean(x),label=round(mean(x,na.rm=T),2)))}

plot2 <- data2 %>%
  ggplot(aes(x=factor(variable, level=unique(variable)), y=value, fill=variable)) +
  geom_boxplot(aes_string(colour="variable", fill="variable"), width=0.7) +
  stat_summary(geom = "crossbar", width=0.7, color="black", fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  xlab("Arrangement") + ylab("Nesting level") +
  stat_summary(fun=mean, geom="point",colour="darkred", size=2) +
  stat_summary(fun.data = fun_mean, geom="text", vjust=1.8) +
  scale_y_continuous(breaks = c(0, 1, 2, 3, 4, 5), limits=c(0,5)) +
  theme_minimal()+ 
  theme(legend.position="none") + 
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors)

print(plot)
print(plot2)

ggsave("plots/bar_levels.eps",
       plot = plot,
       device = "eps",
       scale = 1, units = "cm",
       height=10,
       dpi = 300,
       limitsize = TRUE)

ggsave("plots/box_levels.eps",
       plot = plot2,
       device = "eps",
       scale = 1, units = "cm",
       height = 10,
       dpi = 300,
       limitsize = TRUE)
```

### Task 1.2 - Favoured arrangement comparision
```{r}
getwd()
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(waffle)
library(scales)

favourite <- read_excel("data/data_prepared.xlsx", sheet="task_1_favourite")

data1 <- favourite %>%
  count(`Favourite of proposed`, sort=TRUE) %>%
  mutate(freq = percent(n / sum(n))) %>%
  unite(col=label , `Favourite of proposed`, freq , sep = ", ") %>%
  pull(n, label)

data2 <- favourite %>%
  count(`Favourite overall`, sort=TRUE) %>%
  mutate(freq = percent(n / sum(n))) %>%
  unite(col=label , `Favourite overall`, freq , sep = ", ") %>%
  pull(n, label)

plot1 <- waffle(data1, rows=2,
                colors = c("#4a7c59", "#68b0ab", "#F7ECCA"))
 
plot2 <- waffle(data2, rows=2,
                colors = c("#4a7c59", "#68b0ab", "#F7ECCA", "#8fc0a9", "#c8d5b9"))

plot1
plot2

ggsave("plots/waffle_favourite_of_proposed.eps",
       plot = plot1,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 4,
       limitsize = TRUE)

ggsave("plots/waffle_favourite_overall.eps",
       plot = plot2,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 4,
       limitsize = TRUE)

```
### Task 2 - Manual scheduling evaluation - Scatter plots
```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(scales)
library(ggplot2)
library(stringr)

raw <- read_excel("data/data_prepared.xlsx", sheet="task_2_raw")
#View(raw)
data1 <- raw %>% 
  select(c(1,2:3)) %>%
  pivot_longer(cols = c(`2_1_finish_date_est`, `2_1_finish_date_real`), names_to="variable", values_to="value")
data2 <- raw %>% 
  select(c(1,4:5)) %>%
  pivot_longer(cols = c(`2_2_finish_date_est`, `2_2_finish_date_real`), names_to="variable", values_to="value")
data3 <- raw %>% 
  select(c(1,6:7)) %>%
  pivot_longer(cols = c(`2_1_due_dates_est`, `2_1_due_dates_real`), names_to="variable", values_to="value")
data4 <- raw %>% 
  select(c(1,8:9)) %>%
  pivot_longer(cols = c(`2_2_due_dates_est`, `2_2_due_dates_real`), names_to="variable", values_to="value")

colors1 <- c("#a9ad71", "#a9ad71")
colors2 <- c("#fa9500", "#fa9500")
labels1 <- c("Estimated finish date", "Resulting finish date")
labels2 <- c("Estimated missed due dates", "Resulting missed due dates")


plot1 <- data1 %>%
  ggplot(aes(y=value, x=variable)) +
  geom_line(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) +
  geom_point(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) +
  geom_hline(yintercept=c(as.POSIXct("2021-11-01 18:00:00", tz = "UTC")), linetype="dotted")+
  stat_summary(data=data1, geom = "crossbar", fatten=0, width=0.3, color="black", 
              fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  xlab("") + ylab("Finish date") + 
  scale_y_datetime(breaks = date_breaks('2 hour')) +
  scale_x_discrete(labels = labels1)  +
  theme_minimal() + 
  theme(legend.position="none") + 
  theme(legend.title = element_blank()) + 
  scale_fill_manual(values = colors1) +
  scale_color_manual(values = colors1)

plot2 <- data2 %>%
  ggplot(aes(x=variable, y=value)) +
  geom_line(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) +
  geom_point(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) +  geom_hline(yintercept=c(as.POSIXct("2021-11-05 18:00:00", tz = "UTC")), linetype="dotted")+
  stat_summary(geom = "crossbar", fatten=0, width=0.3, color="black", 
              fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  xlab("") + ylab("Finish date") + 
  scale_y_datetime(breaks = date_breaks('8 hour')) +
  scale_x_discrete(labels = labels1)  +
  theme_minimal() + 
  theme(legend.position="none") + 
  theme(legend.title = element_blank()) + 
  scale_fill_manual(values = colors2) +
  scale_color_manual(values = colors2)

plot3 <- data3 %>%
  ggplot(aes(x=variable, y=value)) +
  geom_line(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) +
  geom_point(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) + 
  geom_hline(yintercept=c(0), linetype="dotted")+
  stat_summary(geom = "crossbar", fatten=0, width=0.3, color="black", 
              fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  xlab("") + ylab("Missed due dates") + 
  scale_y_continuous(breaks = c(0, 1), limits=c(0,1)) +
  scale_x_discrete(labels = str_wrap(labels2, width = 20))  +
  theme_minimal() + 
  theme(legend.position="none") + 
  theme(legend.title = element_blank()) + 
  scale_fill_manual(values = colors1) +
  scale_color_manual(values = colors1)

plot4 <- data4 %>%
  ggplot(aes(x=variable, y=value)) +
  geom_line(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) +
  geom_point(aes(y=value, x=variable, color=variable, group=`Participant ID`), position = position_jitter(w = 0.2, h = 0, seed = 1)) + 
  geom_hline(yintercept=c(2), linetype="dotted")+
  stat_summary(geom = "crossbar", fatten=0, width=0.3, color="black", 
              fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits=c(0,4)) +
  scale_x_discrete(labels = str_wrap(labels2, width = 20))  +
  xlab("") + ylab("Missed due dates") + 
  theme_minimal() + 
  theme(legend.position="none") + 
  theme(legend.title = element_blank()) + 
  scale_fill_manual(values = colors2) +
  scale_color_manual(values = colors2)

plot1
plot2
plot3
plot4

ggsave("plots/scatter_finish_2_1.eps",
       plot = plot1,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 12,
       width = 12,
       limitsize = TRUE)

ggsave("plots/scatter_finish_2_2.eps",
       plot = plot2,
       device = "eps",
       units = "cm",
       scale = 1,
       dpi = 300,
       height = 12,
       width = 12,
       limitsize = TRUE)

ggsave("plots/scatter_due_2_1.eps",
       plot = plot3,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 8,
       width = 10,
       limitsize = TRUE)
ggsave("plots/scatter_due_2_2.eps",
       plot = plot4,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 8,
       width = 10,
       limitsize = TRUE)
```

### Task 2 - Manual scheduling errors
```{r}
# Removing borders on box_plot: http://biochemres.com/beautiful-minimalist-boxplots-with-r-and-ggplot2

getwd()
library(readxl)
library(reshape2)
library(ggplot2)

diff_h <- read_excel("data/data_prepared.xlsx", sheet="task_2_diff_h")
diff_due <- read_excel("data/data_prepared.xlsx", sheet="task_2_diff_due")
diff_order <- read_excel("data/data_prepared.xlsx", sheet="task_2_diff_order")

data_h <- melt(diff_h, id.vars=c("Participant ID", "Type"))
data_due <- melt(diff_due, id.vars=c("Participant ID", "Type"))
data_order <- melt(diff_order, id.vars=c("Participant ID", "Type"))

colors <- c("Task 2.1" = "#a9ad71", "Task 2.2" = "#fa9500")

fun_mean <- function(x){
  return(data.frame(y=mean(x),label=round(mean(x,na.rm=T),2)))}

plot_h <- data_h %>%
  ggplot(aes(x=factor(Type, level=unique(Type)), y=value, fill=variable)) +
  geom_boxplot(aes_string(colour="variable", fill="variable"), width=0.7) +
  stat_summary(geom = "crossbar", width=0.63, position = position_dodge(width = 0.7), color="black", 
               fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  stat_summary(fun=mean, geom="point",colour="darkred", position = position_dodge(width = 0.7)) +
  stat_summary(fun.data = fun_mean, geom="text", size=3, vjust=1.6, position = position_dodge(width = 0.7)) +
  xlab("Error type") + ylab("Working hours") + 
  theme_minimal() + 
  theme(legend.title = element_blank()) + 
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
  guides(fill="none")

plot_due <- data_due %>%
  ggplot(aes(x=factor(Type, level=unique(Type)), y=value, fill=variable)) + 
  geom_boxplot(aes_string(colour="variable", fill="variable"), width=0.7) +
  stat_summary(geom = "crossbar", width=0.63, position = position_dodge(width = 0.7), color="black", 
               fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  stat_summary(fun=mean, geom="point",colour="darkred", position = position_dodge(width = 0.7)) +
  stat_summary(fun.data = fun_mean, geom="text", size=3, vjust=1.6, position = position_dodge(width = 0.7)) +
  xlab("Error type") + ylab("Missed due dates") +
  theme_minimal() + 
  theme(legend.title = element_blank()) +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
  guides(fill="none")

summary(data_order)
plot_order <- data_order %>%
  ggplot(aes(x=factor(Type, level=unique(Type)), y=value, fill=variable)) + 
  geom_boxplot(aes_string(colour="variable", fill="variable"), width=0.7) +
  stat_summary(geom = "crossbar", width=0.63, position = position_dodge(width = 0.7), color="black", 
               fun.data = function(x){ return(c(y=median(x), ymin=median(x), ymax=median(x))) }) +
  stat_summary(fun=mean, geom="point",colour="darkred", position = position_dodge(width = 0.7)) +
  stat_summary(fun.data = fun_mean, geom="text", size=3, vjust=1.6, position = position_dodge(width = 0.7)) +
  scale_y_continuous(breaks = c(.2, .4, .6, .8, 1), limits=c(0,1)) +
  xlab("Similarity of manual order") + ylab("Similarity measure") + 
  theme_minimal() + 
  theme(legend.title = element_blank()) +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
  guides(fill="none")

plot_h
plot_due
plot_order

ggsave("plots/box_diff_h.eps",
       plot = plot_h,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 10,
       limitsize = TRUE)
ggsave("plots/box_diff_due.eps",
       plot = plot_due,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 10,
       limitsize = TRUE)
ggsave("plots/box_diff_order.eps",
       plot = plot_order,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       height = 10,
       limitsize = TRUE)
```

### Task 1 - Likert type questions
```{r}
library(dplyr)
library(readxl)
library(likert)

likert1 <- read_excel("data/data_prepared.xlsx", sheet="likert_1")
likert1 <- likert1 %>% select(-c(`Participant ID`))

questions <- c(
  "I understood what my task was about.", 
  "The software supported me visualizing the project.", 
  "The arrangement I created matches my mental image of the project."
  )

data <- likert1 %>%
    mutate_all(~dplyr::recode(., `1` = "Strongly disagree", `2` = "Disagree", `3` = "Neutral", `4` = "Agree", `5` = "Strongly agree")) %>%
    lapply(factor, levels= c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"), ordered = TRUE) %>%
    as.data.frame()  %>% 
  rename(
      !!questions[1] := "LTQ1A",
      !!questions[2] := "LTQ1B",
      !!questions[3] := "LTQ1C"
    ) 

plot <- likert(data) %>%
  likert.bar.plot(wrap=25, group.order = names(data)) +
  theme_minimal() + 
  theme(axis.text.y = element_text(size = 8), legend.position = "bottom", legend.text=element_text(size = 8))

plot(plot)

ggsave("plots/likert_1.eps",
       plot = plot,
       device = "eps",
       scale = 1, units = "cm",
       height = 8,
       dpi = 300,
       limitsize = TRUE)
```

### Task 2 - Likert type questions
```{r}
library(dplyr)
library(readxl)
library(likert)

likert2 <- read_excel("data/data_prepared.xlsx", sheet="likert_2")
likert2 <- likert2 %>% select(-c(`Participant ID`))

questions <- c(
  "I feel patronized by the software making the planning for me.",
  "I find the proposal easy to perceive.",
  "I find the proposal intelligable.",
  "I trust the proposal to be better than my manual planning.",
  "I would find an automatic planning feature like this to be helpful.",
  "It is likely that I would use an automatic planning feature like this.",
  "If my privacy is guaranteed, I am generally open to intelligent features in a software like this."
  )

data <- likert2 %>%
    mutate_all(~dplyr::recode(., `1` = "Strongly disagree", `2` = "Disagree", `3` = "Neutral", `4` = "Agree", `5` = "Strongly agree")) %>%
    lapply(factor, levels= c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")) %>%
    as.data.frame()  %>% 
  rename(
      !!questions[1] := "LTQ2A",
      !!questions[2] := "LTQ2B",
      !!questions[3] := "LTQ2C",
      !!questions[4] := "LTQ2D",
      !!questions[5] := "LTQ2E",      
      !!questions[6] := "LTQ2F",
      !!questions[7] := "LTQ2G",
    ) 

plot <- likert(data) %>%
  likert.bar.plot(wrap=30, ordered=FALSE, group.order=names(data)) +
  theme_minimal() + 
  theme(axis.text.y = element_text(size = 8), legend.position = "bottom", legend.text=element_text(size = 8))

print(plot)

ggsave("plots/likert_2.eps",
       plot = plot,
       device = "eps",
       scale = 1, units = "cm",
       dpi = 300,
       limitsize = TRUE)
```

### General - Likert type questions
```{r}
library(dplyr)
library(readxl)
library(likert)

likert3 <- read_excel("data/data_prepared.xlsx", sheet="likert_3")
likert3 <- likert3 %>% select(-c(`Participant ID`))

questions <- c(
  "I found the interface of the software easy to understand.",
  "The features of the software were clear to me. I understand what can be done using the features.",
  "I liked the possibility to arrange elements (boards, lists, items) in an arbitrarily nested way."
  )

data <- likert3 %>%
    mutate_all(~dplyr::recode(., `1` = "Strongly disagree", `2` = "Disagree", `3` = "Neutral", `4` = "Agree", `5` = "Strongly agree")) %>%
    lapply(factor, levels= c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"), ordered = TRUE) %>%
    as.data.frame()  %>% 
  rename(
      !!questions[1] := "LTQ3A",
      !!questions[2] := "LTQ3B",
      !!questions[3] := "LTQ3C"
    ) 

plot <- likert(data) %>%
  likert.bar.plot(wrap=25, group.order = names(data)) +
  theme_minimal() + 
  theme(axis.text.y = element_text(size = 8), legend.position = "bottom", legend.text=element_text(size = 8))

plot(plot)

ggsave("plots/likert_3.eps",
       plot = plot,
       device = "eps",
       scale = 1, units = "cm",
       height = 8,
       dpi = 300,
       limitsize = TRUE)
```
## Statistic testing

### Task 1.1 Explorative correlation testing experience -> number of events
```{r}
getwd()
library(readxl)
library(PerformanceAnalytics)
events <- read_excel("data/data_prepared.xlsx", sheet="task_1_events")

data <- events[, c(2:14)]
chart.Correlation(data, histogram = TRUE, method = "pearson")

cor.test(events$`Used before`, events$Total)
cor.test(events$`Used before`, events$MOVE)
cor.test(events$`Used before`, events$CREATE)


cor.test(events$`Prior experience`, events$Total)
cor.test(events$`Prior experience`, events$MOVE)
cor.test(events$`Prior experience`, events$CREATE)
plot(events$`Favourite of proposed`, events$`CONVERT`)
```

### Task 1 - Do the used levels significantly deviate from the standard level of 2?
```{r}
library(readxl)
library(stats)
library(ggpubr)

level <- read_excel("data/data_prepared.xlsx", sheet="task_1_level")

standard_lvl <- 2

# Is data normally distributed? 
# If yes -> one-sample t-test (http://www.sthda.com/english/wiki/one-sample-t-test-in-r)
# if no -> One-sample Wilcoxon signed rank test (http://www.sthda.com/english/wiki/wiki.php?title=one-sample-wilcoxon-signed-rank-test-in-r)

# 1. sample size < 30 -> Check if data is normally distributed via 
# 1.1 Shapiro-Wilk's test 
# 1.2 Normal Q-Q plot
# 2. Check for outliers -> Inspection of Boxplot 
# 3. Perform t-test

# Personal nesting levels 
# Shapiro-Wilk's test & Normal Q-Q plot -> data is normally distributed
shapiro.test(level$Personal)
ggqqplot(level$Personal)
# one-sample t-test -> Is MEAN greater then standard_lvl?
t.test(level$Personal, alternative = c("greater"), mu=standard_lvl)


# Favorite of proposed nesting levels
# Shapiro-Wilk's test -> data is not normally distributed
shapiro.test(level$`Favourite of proposed`)
# One-sample Wilcoxon signed rank test -> Is MEDIAN greater then standard_lvl?
wilcox.test(level$`Favourite of proposed`, alternative="greater", mu=standard_lvl)

# Favorite overall nesting levels
# Shapiro-Wilk's test -> data is not normally distributed
shapiro.test(level$`Favourite overall`)
# One-sample Wilcoxon signed rank test -> Is MEDIAN greater then standard_lvl?
wilcox.test(level$`Favourite overall`, alternative="greater", mu=standard_lvl)
```

### Task 1 - Significance of difference between number of actions with/without prior experience
```{r}
library(readxl)
library(dplyr)
library(stats)
library(ggpubr)
events <- read_excel("data/data_prepared.xlsx", sheet="task_1_events")

# Are both independent samples normally distributed and variances no difer significantly?
# If yes -> Unpaired Two-Samples Wilcoxon Test (http://www.sthda.com/english/wiki/unpaired-two-samples-t-test-in-r)
# If no -> Unpaired Two-Samples T-test (http://www.sthda.com/english/wiki/unpaired-two-samples-wilcoxon-test-in-r)


exp <- events %>% filter(`Used before` == 1)
no_exp <- events %>% filter(`Used before` == 0)

shapiro.test(exp$Total)
shapiro.test(no_exp$Total)
var.test(exp$Total, no_exp$Total)
t.test(exp$Total, no_exp$Total, var.equal = TRUE, alternative = "greater")

shapiro.test(exp$MOVE)
shapiro.test(no_exp$MOVE)
var.test(exp$MOVE, no_exp$MOVE)
t.test(exp$MOVE, no_exp$MOVE, var.equal = TRUE, alternative = "greater")

shapiro.test(exp$CREATE)
shapiro.test(no_exp$CREATE)
var.test(exp$CREATE, no_exp$CREATE)
wilcox.test(exp$CREATE, no_exp$CREATE, var.equal = TRUE, alternative = "greater")

shapiro.test(exp$REORDER)
shapiro.test(no_exp$REORDER)
var.test(exp$REORDER, no_exp$REORDER)
t.test(exp$REORDER, no_exp$REORDER, var.equal = TRUE, alternative = "less")

shapiro.test(exp$CONVERT)
shapiro.test(no_exp$CONVERT)
var.test(exp$CONVERT, no_exp$CONVERT)
wilcox.test(exp$CONVERT, no_exp$CONVERT, var.equal = TRUE, alternative = "less")
```
### Task 2 - Significance of true error
```{r}
library(readxl)
library(stats)
library(ggpubr)

raw <- read_excel("data/data_prepared.xlsx", sheet="task_2_raw")

# Finish date
opt_finish_date_2_1 <- as.numeric(as.POSIXct("2021-11-01 18:00:00", tz = "UTC"))
opt_finish_date_2_2 <- as.numeric(as.POSIXct("2021-11-05 18:00:00", tz = "UTC"))

real_finish_date_2_1 <- as.numeric(raw$`2_1_finish_date_real`)
real_finish_date_2_2 <- as.numeric(raw$`2_2_finish_date_real`)

shapiro.test(real_finish_date_2_1)
ggqqplot(real_finish_date_2_1)
wilcox.test(real_finish_date_2_1, alternative="two.sided", mu=opt_finish_date_2_1)
median(raw$`2_1_finish_date_real`)

shapiro.test(real_finish_date_2_2)
ggqqplot(real_finish_date_2_2)
wilcox.test(real_finish_date_2_2, alternative="greater", mu=opt_finish_date_2_2)
median(raw$`2_2_finish_date_real`)


# Due date
opt_due_dates_2_1 <- 0
opt_due_dates_2_2 <- 2

shapiro.test(raw$`2_1_due_dates_real`)
wilcox.test(level$`2_1_due_dates_real`, alternative="two.sided", mu=opt_due_dates_2_1)
median(raw$`2_1_due_dates_real`)

shapiro.test(raw$`2_2_due_dates_real`)
wilcox.test(level$`2_2_due_dates_real`, alternative="greater", mu=opt_due_dates_2_2)
median(raw$`2_2_due_dates_real`)


t.test(level$Personal, alternative="greater", mu=standard_lvl)
t.test(level$`Favourite of proposed`, alternative="greater", mu=standard_lvl)
t.test(level$`Favourite overall`, alternative="greater", mu=standard_lvl)
```

### Task 2 - Significance of assessment error
```{r}
library(readxl)
library(stats)
library(ggpubr)

raw <- read_excel("data/data_prepared.xlsx", sheet="task_2_raw")

# Is difference between pairs normally distributed?
# If yes -> Paired Samples T-test (http://www.sthda.com/english/wiki/paired-samples-t-test-in-r)
# If no -> Paired Samples Wilcoxon Test (http://www.sthda.com/english/wiki/paired-samples-wilcoxon-test-in-r)

# Finish date
est_finish_date_2_1 <- as.numeric(raw$`2_1_finish_date_est`)
est_finish_date_2_2 <- as.numeric(raw$`2_2_finish_date_est`)

real_finish_date_2_1 <- as.numeric(raw$`2_1_finish_date_real`)
real_finish_date_2_2 <- as.numeric(raw$`2_2_finish_date_real`)


diff_2_1 <- est_finish_date_2_1 - real_finish_date_2_1
diff_2_2 <- est_finish_date_2_2 - real_finish_date_2_2

shapiro.test(diff_2_1)
wilcox.test(est_finish_date_2_1, real_finish_date_2_1, paired = TRUE,
       alternative = "two.sided")
median(raw$`2_1_finish_date_est`)
median(raw$`2_1_finish_date_real`)

shapiro.test(diff_2_2)
wilcox.test(est_finish_date_2_2, real_finish_date_2_2, paired = TRUE,
       alternative = "less")
median(raw$`2_2_finish_date_est`)
median(raw$`2_2_finish_date_real`)


# Due date
est_due_dates_2_1 <- as.numeric(raw$`2_1_due_dates_est`)
est_due_dates_2_2 <- as.numeric(raw$`2_2_due_dates_est`)

real_due_dates_2_1 <- as.numeric(raw$`2_1_due_dates_real`)
real_due_dates_2_2 <- as.numeric(raw$`2_2_due_dates_real`)

diff_2_1 <- est_due_dates_2_1 - real_due_dates_2_1
diff_2_2 <- est_due_dates_2_2 - real_due_dates_2_2

shapiro.test(diff_2_1)
wilcox.test(est_due_dates_2_1, real_due_dates_2_1, paired = TRUE,
       alternative = "two.sided")
median(est_due_dates_2_1)
median(real_due_dates_2_1)

diff_2_2
shapiro.test(diff_2_2)
ggqqplot(diff_2_2)
t.test(est_due_dates_2_2, real_due_dates_2_2, paired = TRUE,
       alternative = "less")
mean(est_due_dates_2_2)
mean(real_due_dates_2_2)
```